Blocking-resistant communication\\through domain fronting

### 2015-02-07 docs/fronting.tex
Move commented JumpBox ref to the TLS camouflage section.
This is where it belongs if I decide to put it in.
Hack related work.
Make active probing a peer of address blocking and content blocking.

Broadly speaking, there are two main challenges in circumvention:
blocking by content and blocking by address.
Blocking by content is based on \emph{what you say},
and blocking by address is based on \emph{whom you talk to}.
A content-blocking censor inspects packets and payloads,
looking, for example, for forbidden protocols or keywords.
Content-based blocking is sometimes called deep packet inspection (DPI).
An address-blocking censor forbids all communication with certain
addresses, for example IP addresses and domain names, regardless of
the contents of the communication.
A savvy censor will use both means of censorship, and
effective circumvention requires countering both.

To the above challenges we add a related one, active probing.
An active-probing censor does not merely passively observe traffic:
it injects its own traffic,
acting as if it were an ordinary client and connecting to suspected
proxy servers to see how they respond.
Then a connection is successful, the server can be blacklisted.
Active probing is a precise means of identifying whether a server belongs to a circumvention system,
even when a protocol is hard to detect on the wire.
Winter and Lindskog~\cite{foci12-winter} confirmed an earlier discovery of
Wilde~\cite{wilde} that China's Great Firewall identifies Tor bridges
by issuing scans that follow up on observed client connections, to discover
whether a server speaks the Tor protocol.

There are two general strategies for countering content-based blocking.
The first is to make traffic look unlike
anything forbidden by the censor; that is, fail to match a blacklist. The second is
to resemble a protocol that is explicitly allowed by the censor; that is, match a whitelist.
Following the first strategy are the so-called ``look-like-nothing'' transports whose
payloads are indistinguishable from a uniformly random byte stream.
Examples of look-like-nothing transports are
obfuscated-openssh~\cite{obfuscated-openssh} and its string of successors:
obfs2~\cite{obfs2}, obfs3~\cite{obfs3}, ScrambleSuit~\cite{scramblesuit}, and obfs4~\cite{obfs4}.
They all work by re-encrypting
an underlying stream so that there remains no plaintext components,
not even in the handshake and key exchange.
obfs2, introduced in early 2012~\cite{obfsproxy-arms-race},
used a fairly weak key exchange that can be detected passively;
it is now deprecated and little used.
obfs3 is currently Tor's most-used transport~\cite{metrics-obfs3}.
It improves on obfs2 with a Diffie--Hellman key exchange,
public keys being encoded so as to be indistinguishable from random binary strings.
ScrambleSuit and obfs4 add resistance to active probing:
the server accepts a TCP connection but does not send a reply
until the client proves knowledge of a secret shared out of band.
They additionally additionally obscure the traffic signature of the underlying stream
by modifying packet lengths and timing.

The other strategy against DPI is the steganographic one: look like
something the censor does not block.
fteproxy~\cite{fte} uses format-transforming encryption to encode data into strings
that match a given regular expression,
for example a regular-expression approximation of HTTP.
StegoTorus~\cite{stegotorus}
transforms traffic to look like a cover protocol
using a variety of special-purpose encoders.
Code Talker
Tunnel (formerly called SkypeMorph)~\cite{skypemorph} mimics a Skype video call.
FreeWave~\cite{freewave} encodes a stream as an acoustic signal
and sends it over VoIP to a proxy.
Dust~\cite{dust} uses encryption to hide static byte patterns and then
shapes statistical features such as packet lengths and byte frequencies so that they
match given distributions.

Houmansadr et~al.~\cite{parrot} evaluate ``parrot'' systems that imitate another protocol
and conclude that unobservability by imitation is fundamentally flawed.
To fully mimic a complex and sometimes proprietary protocol like Skype
is difficult,
because the system must imitate not only the normal operation of the protocol,
but also its reaction to errors,
its typical traffic patterns, and quirks of implementations.
Geddes et~al.~\cite{acks}
demonstrate that even non-parrot systems may be vulnerable to
attacks that disrupt circumvention while having little effect
on ordinary traffic.
Their examination includes VoIP protocols,
in which packet loss and duplication are acceptable.
The censor may, for example, strategically drop certain packets
in order to disrupt a covert channel, without much harming ordinary VoIP calls.
\vp{The above could be compressed somewhat to save room}

The other grand challenge of proxy-based circumvention is address-based blocking.
Tor has long faced the problem of the blocking of its relays,
the addresses of which appear in a public directory.
In response, Tor began to reserve a portion of its
new relays as secret ``bridges''~\cite{tor-blocking}
whose addresses are not publicly known.
BridgeDB, the database of secret bridges,
carefully distributes bridge addresses
so that anyone can learn a few bridges, but it is hard to learn all of them.
BridgeDB uses CAPTCHAs and other rate-limiting measures,
and over short time periods,
always returns the same set of bridges to the same requester,
preventing enumeration by simple repeated queries.
BridgeDB is also capable of distributing the addresses
of obfuscated bridges (obfs3 or ScrambleSuit);
the combination
of careful bridge address distribution and obfuscated protocols
gives Tor's system a realistic claim to addressing both main challenges of circumvention.
Address distribution appears to be the weaker side of the defense,
as evidenced by real-world censors' apparent preference for
blocking bridge addresses over real-time DPI-based blocking~\cite{foci12-winter}.

@@

Flash proxy~\cite{flashproxy} resists address blocking by
conscripting web users as temporary proxies.
Each JavaScript-based proxy lasts only as long as a
user stays on a web page, so the pool of proxies is constantly changing.
If one of them is blocked, there is soon another to replace it.
Flash proxy's approach to address blocking is
the opposite of \meek's:
where flash proxy uses many cheap, disposable, individually blockable proxies,
\meek uses just a few high-value front domains on hard-to-block network infrastructure.
A drawback with flash proxy's use of the browser is that
the client must be able to receive a TCP connection; in particular it
must not be behind network address translation~(NAT), which limits flash proxy's usefulness.
Part of the flash proxy protocol requires the client to send
a small amount of unblockable data in a process called rendezvous.
The default rendezvous mechanism has used domain fronting through App Engine since 2013~\cite{flashproxy-reg-appspot}.
Flash proxy itself does nothing to defend against DPI.
Connections between censored clients and browser-based proxies use
WebSocket, a meta-protocol running on HTTP,
but inside the WebSocket framing is the ordinary Tor protocol.
% There exists a prototype transport that attempts to get both
% content-based and address-based blocking resistance by obfuscating traffic
% with obfsproxy before sending it through flash proxy~\cite{obfs-flash}.
% However it is limited because it is not
% possible to obfuscate the outermost WebSocket layer;
% the censor could decide simply to block all WebSocket.

A technique known as OSS~\cite{oss} (for
``online scanning service'') bounces messages
through web services that are capable of making HTTP requests.
For example, a censored client may ask an HTTPS-based online translation service to
translate the web page at \urll{http://forbidden.example/}\textsl{data},
where ``\textsl{data}'' is the URL-embedded message the client wants to send.
The translation service requests the URL,
unwittingly sending the message on behalf of the client.
OSS shares certain similarities with domain fronting:
an unblockable web service takes the place of the front domain,
and the destination of the communication is embedded somewhere in an HTTPS query
rather than in the Host header.
\vp{Sketch the limitations of this approach}

Decoy routing~\cite{decoyrouting}
is a technique that puts
proxies in the middle of network paths, rather than at the ends.
For this reason, it is also called end-to-middle proxying.
Realizations of decoy routing include Telex~\cite{telex},
Cirripede~\cite{cirripede}, and TapDance~\cite{tapdance}.
Decoy routing asks friendly ISPs to deploy special routers that reside
on network paths between censored users and uncensored ``decoy'' Internet destinations.
Circumvention traffic is ``tagged'' in a way that is detectable only
by the special routers, and not by the censor.
On receiving a tagged communication, the router shunts it away from its apparent, \emph{overt destination}
and toward a censored, \emph{covert destination}.
Domain fronting is similar in spirit to decoy routing:
think of domain fronting as decoy routing at the application layer.
In place of a router, domain fronting has a frontend server;
in place of the overt destination is the front domain.
Both systems tag flows in a way that is invisible to the censor:
decoy routing uses, for example, a hash embedded in a client nonce,
while fronting uses the HTTP Host header, encrypted within HTTPS.
Fronting has the advantage that it does not require active cooperation by network intermediaries.

@@

To our knowledge,
the earliest use of domain fronting for circumvention
was by GoAgent~\cite{goagent},
a tool based on App Engine and
once widely used in China.
Traffic is fronted by the Google frontend server,
using the ``domainless'' fronting model without SNI,
and delivered to its destination by a specialized app running on App Engine.
GoAgent does not use an additional general-purpose proxy after fronting;
rather, HTTP and HTTPS URLs are fetched directly from the App Engine servers.
Because of that, GoAgent is limited to carrying HTTP and HTTPS traffic only,
and the contents of all communications are revealed to Google.
Users of GoAgent upload
their own personal copy of the proxy code to App Engine,
which is free of charge to use as long as they do not exceed a bandwidth quota.
According to a May 2013 survey~\cite{collateral-freedom},
GoAgent was the circumvention tool most used in
China, with 35\% of survey respondents having used it in the previous month.
This figure is higher than that of paid~(29\%) and free VPNs~(18\%), and far
above that of other special-purpose tools like Tor~(2.9\%) and Psiphon~(2.5\%).
Use of GoAgent in China was disrupted starting in the beginning of June~2014,
when all Google services were blocked~\cite{cn-google-block}.
\meek over App Engine was similarly affected.
\vp{Add mention of what \meek platforms still worked.}
% Users identified reliability, speed, and ease of installation as the most important features of a circumvention tool.

>>>>

Broadly speaking, there are three main challenges in proxy-based circumvention:
blocking by content, blocking by address, and active probing.
Blocking by content is based on \emph{what you say},
blocking by address is based on \emph{whom you talk to},
and active probing means \emph{the censor acts as a client}.
A savvy censor will employ all these techniques, and
effective circumvention requires countering them all.

A content-blocking censor inspects packets and payloads,
looking, for example, for forbidden protocols or keywords.
Content-based blocking is sometimes called deep packet inspection (DPI).
An address-blocking censor forbids all communication with certain
addresses, for example IP addresses and domain names, regardless of
the contents of the communication.
An active-probing censor does not limit itself to observation and manipulation
only of user-induced traffic.
It sends its own proxy requests (active probes),
either proactively or on demand in response to observed traffic,
and blacklists any proxies it finds thereby.
Active probing is a precise means of identifying whether a server belongs to a circumvention system,
even when a protocol is hard to detect on the wire---in this way it can
regarded as a way of reducing accidental overblocking.
Winter and Lindskog~\cite{foci12-winter} confirmed an earlier discovery of
Wilde~\cite{wilde} that China's Great Firewall discovers secret Tor bridges
by issuing its own followup scans after observing a suspected Tor connection.

There are two general strategies for countering content-based blocking.
The first is to look unlike anything the censor blocks;
the second is to look like something the censor allows.
Following the first strategy are the so-called ``look-like-nothing'' transports whose
payloads are indistinguishable from a uniformly random byte stream.
Examples of look-like-nothing transports are
obfuscated-openssh~\cite{obfuscated-openssh} and its string of successors:
obfs2~\cite{obfs2}, obfs3~\cite{obfs3}, ScrambleSuit~\cite{scramblesuit}, and obfs4~\cite{obfs4}.
They all work by re-encrypting
an underlying stream so that there remains no plaintext components,
not even in the handshake and key exchange.
obfs2, introduced in early 2012~\cite{obfsproxy-arms-race},
used a fairly weak key exchange that can be detected passively;
it is now deprecated and little used.
obfs3 is currently Tor's most-used transport~\cite{metrics-obfs3}.
It improves on obfs2 with a Diffie--Hellman key exchange,
public keys being encoded so as to be indistinguishable from random binary strings.
ScrambleSuit and obfs4 add resistance to active probing:
the server accepts a TCP connection but does not send a reply
until the client proves knowledge of a secret shared out of band.
They additionally additionally obscure the traffic signature of the underlying stream
by modifying packet lengths and timing.

The other strategy against DPI is the steganographic one: look like
something allowed by the censor.
fteproxy~\cite{fte} uses format-transforming encryption to encode data into strings
that match a given regular expression,
for example a regular-expression approximation of HTTP.
StegoTorus~\cite{stegotorus}
transforms traffic to look like a cover protocol
using a variety of special-purpose encoders.
Code Talker
Tunnel (formerly called SkypeMorph)~\cite{skypemorph} mimics a Skype video call.
FreeWave~\cite{freewave} encodes a stream as an acoustic signal
and sends it over VoIP to a proxy.
Dust~\cite{dust} uses encryption to hide static byte patterns and then
shapes statistical features such as packet lengths and byte frequencies so that they
match given distributions.

Houmansadr et~al.~\cite{parrot} evaluate ``parrot'' systems that imitate another protocol
and conclude that unobservability by imitation is fundamentally flawed.
To fully mimic a complex and sometimes proprietary protocol like Skype
is difficult,
because the system must imitate not only the normal operation of the protocol,
but also its reaction to errors,
its typical traffic patterns, and quirks of implementations.
Geddes et~al.~\cite{acks}
demonstrate that even non-parrot systems may be vulnerable to
attacks that disrupt circumvention while having little effect
on ordinary traffic.
Their examination includes VoIP protocols,
in which packet loss and duplication are acceptable.
The censor may, for example, strategically drop certain packets
in order to disrupt a covert channel, without much harming ordinary VoIP calls.

The challenge of address-based blocking is a difficult one
that has inspired various creative circumvention ideas.
Tor has long faced the problem of the blocking of its relays,
the addresses of which appear in a public directory.
In response, Tor began to reserve a portion of its
relays as secret ``bridges''~\cite{tor-blocking}
whose addresses are not publicly known.
BridgeDB, the database of secret bridges,
carefully distributes addresses
so that anyone may learn a few bridges, but it is hard to enumerate all of them.
BridgeDB uses CAPTCHAs and other rate-limiting measures,
and over short time periods,
always returns the same bridges to the same requester,
preventing enumeration by simple repeated queries.
BridgeDB is also capable of distributing the addresses
of obfuscated bridges (currently obfs3, obfs4, ScrambleSuit, and fteproxy),
granting some address-blocking resistance to those systems that otherwise lack it.
% Address distribution appears to be the weaker side of the defense,
% as evidenced by real-world censors' apparent preference for
% blocking bridge addresses over real-time DPI-based blocking~\cite{foci12-winter}.

@@

Flash proxy~\cite{flashproxy} resists address blocking by
conscripting web users as temporary proxies.
Each JavaScript-based proxy lasts only as long as a
user stays on a web page, so the pool of proxies is constantly changing.
If one of them is blocked, there is soon another to replace it.
Flash proxy's approach to address blocking is
the opposite of domain fronting's:
where flash proxy uses many cheap, disposable, individually blockable proxies,
domain fronting uses just a few high-value front domains on hard-to-block network infrastructure.
A drawback with flash proxy's use of the browser is that
the client must be able to receive a TCP connection; in particular it
must not be behind network address translation~(NAT), which limits flash proxy's usefulness.
Part of the flash proxy protocol requires the client to send
a small amount of unblockable data in a process called rendezvous.
The default rendezvous mechanism has been domain fronting through Google App Engine since 2013~\cite{flashproxy-reg-appspot}.
Flash proxy itself does nothing to defend against DPI.
Connections between censored clients and browser-based proxies use
WebSocket, a meta-protocol running on HTTP,
but inside the WebSocket framing is the ordinary TLS-based Tor protocol.
% There exists a prototype transport that attempts to get both
% content-based and address-based blocking resistance by obfuscating traffic
% with obfsproxy before sending it through flash proxy~\cite{obfs-flash}.
% However it is limited because it is not
% possible to obfuscate the outermost WebSocket layer;
% the censor could decide simply to block all WebSocket.

A technique known as OSS~\cite{oss} (for
``online scanning service'') bounces messages
through web services that are capable of making HTTP requests.
For example, a censored client may ask an HTTPS-based online translation service to
translate the web page at \urll{http://forbidden.example/}\textsl{data},
where ``\textsl{data}'' is the URL-embedded message the client wants to send.
The translation service requests the URL,
unwittingly sending the message on behalf of the client.
OSS shares certain similarities with domain fronting:
a hard-to-block web service takes the place of the front domain,
and the destination is embedded somewhere in an HTTPS query
rather than in the Host header.
OSS has high overhead and low capacity,
and suffers the same limitations with NAT on the client that flash proxy has.

Decoy routing~\cite{decoyrouting}
is a technique that puts
proxies in the middle of network paths, rather than at the ends.
For this reason, it is also called end-to-middle proxying.
Realizations of decoy routing include Telex~\cite{telex},
Cirripede~\cite{cirripede}, and TapDance~\cite{tapdance}.
Decoy routing asks friendly ISPs to deploy special routers that reside
on network paths between censored users and uncensored ``decoy'' Internet destinations.
Circumvention traffic is ``tagged'' in a way that is detectable only
by the special routers, and not by the censor.
On receiving a tagged communication, the router shunts it away from its apparent, \emph{overt destination}
and toward a censored, \emph{covert destination}.
Domain fronting is similar in spirit to decoy routing:
think of domain fronting as decoy routing at the application layer.
In place of a router, domain fronting has a frontend server;
in place of the overt destination is the front domain.
Both systems tag flows in a way that is invisible to the censor:
decoy routing uses, for example, a hash embedded in a client nonce,
while fronting uses the HTTP Host header, encrypted within HTTPS.
Fronting has the advantage that it does not require cooperation by network intermediaries.

@@

To our knowledge,
the earliest use of domain fronting for circumvention
was by GoAgent~\cite{goagent},
a tool based on Google App Engine and
once widely used in China.
Users of GoAgent upload
a personal copy of the proxy code to App Engine,
where it runs on a subdomain of \urll{appspot.com}.
In order to reach \urll{appspot.com},
GoAgent fronts through a Google IP address,
using the ``domainless'' model without SNI.
GoAgent does not use an additional general-purpose proxy after fronting;
rather, it fetches URLs directly from the App Engine servers.
Because of that, GoAgent does not support protocols other than HTTP and HTTPS,
and the end-to-end security of HTTPS is lost,
as web pages exist in plaintext on the App Engine servers before being re-encrypted back to the client.
App Engine is free to use under a daily bandwidth quota of 1~GB.
According to a May 2013 survey~\cite{collateral-freedom},
GoAgent was the most-used circumvention tool in
China, with 35\% of survey respondents having used it in the previous month.
It ranked higher than paid~(29\%) and free VPNs~(18\%), and far
above special-purpose tools like Tor~(2.9\%) and Psiphon~(2.5\%).
Use of GoAgent in China was disrupted starting in the beginning of June~2014,
when all Google services were blocked~\cite{cn-google-block}.
The block also affected meek, the subject of Section~\ref{sec:deploy-tor},
when used with App Engine, though it continued to work in China over the alternate backends
Amazon CloudFront and Microsoft Azure.
